### 2025-01-24 analysis/analysis.qmd
fix(analysis): aggregate performance across models:  bhuvanakumar2023em and nguyen2017an

# yang2021an needs to be encoded for classification (currently just regression)
C_summary <- read.csv("C_summary.csv")
C_classes <- read.csv("C_study_class_n.csv")

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)

>>>>

# yang2021an needs to be encoded for classification (currently just regression)
C_summary <- read.csv("C_summary.csv")

# 2025-01-24: averaging valence and arousal for this study, which makes the max equivalent to both the mean and median (two models: one valence, one arousal)
C_summary[C_summary$citekey == "nguyen2017an",]$valuesMax <- C_summary[C_summary$citekey == "nguyen2017an",]$valuesMean

# 2025-01-24: averaging across quadrants for bhuvanakumar study
# subset study
bhuvanakumar <- subset(
  C_studies, 
  stringr::str_detect(
    C_studies$citekey,
    "bhuvanakumar"
    )
)
# group by algorithm to average across the four quadrants
bhuvanakumar$model_algorithm <- substr(
  bhuvanakumar$model_id, 
  1, 
  4
)
# take the average for each algorithm
bhuvanakumar |> 
  group_by(model_algorithm) |>
  mutate(values = mean(values)) -> bhuvanakumar
# overwrite values in C_summary
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMean <- mean(unique(bhuvanakumar$values))
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMedian <- median(unique(bhuvanakumar$values))
C_summary[C_summary$citekey == "bhuvanakumar2023em",]$valuesMax <- max(unique(bhuvanakumar$values))

remove(bhuvanakumar)

C_classes <- read.csv("C_study_class_n.csv")

@@

```{r}
#| eval: false
m.cor_subgroups <- update(m.cor, 
#       subgroup = model_class_id, 
#       subgroup = journal_type, 
#       subgroup = stimulus_genre_mixed, 
       tau.common = FALSE,
       prediction = TRUE)
